---
title: "Brandon P. Labbree's CV"
author: Brandon P. Labbree
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
  cache_data:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(pacman)

# library(tidyverse)
# library(icons)
# library(magrittr)


source("cv_printing_functions.r")
# remotes::install_github("mitchelloharawild/icons")
# devtools::install_github("nstrayer/datadrivencv")
 p_load(magrittr, datadrivencv,icons, tidyverse)


# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1Mf3ChHQY-MTwWxH8oXrBvGDjAcl6kgyVzm9eOyuGAV0/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

current_date <- Sys.time()
current_date <- format(current_date,format='%Y%m%d')

basename <- paste0("Labbree_CV_",current_date, sep="")

urlString <- paste("https://github.com/blabbree/CV/tree/main/PDF/",basename,".pdf",sep="")

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r eval=FALSE}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
if(params$pdf_mode == FALSE){
datadrivencv::build_network_logo(CV$entries_data)}
```


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at ",urlString)
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](",urlString,")")
}
```

**Contact** {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```





Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available [on github.com/blabbree/CV](https://github.com/blabbree/CV).

Last updated on `r Sys.Date()`.



Main
================================================================================

Brandon P. Labbree {#title}
--------------------------------------------------------------------------------

_**`r format(Sys.time(), '%B %d, %Y %I:%M:%S %p')`**_

```{r}

# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



**Education** {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```



**Research Experience** {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```



<!-- Industry Experience {data-icon=suitcase} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ::: aside -->
<!-- ```{r} -->
<!-- CV %<>% print_text_block('industy_experience_aside') -->
<!-- ``` -->
<!-- ::: -->

<!-- ```{r} -->
<!-- CV %<>% print_section('industry_positions') -->
<!-- ``` -->

<!-- These breaks just force a new page so section doesnt get cut off -->
<!-- <br> -->
<!-- <br> -->
<!-- <br> -->

**Teaching Experience** {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

<!-- ::: aside -->
<!-- ```{r} -->
<!-- CV %<>% print_text_block('teaching_experience_aside') -->
<!-- ``` -->
<!-- ::: -->

```{r}
CV %<>% print_section('teaching_positions')
```



<!-- Selected Data Science Writing {data-icon=chart-line} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ::: aside -->
<!-- ```{r} -->
<!-- CV %<>% print_text_block('data_science_writing_aside') -->
<!-- ``` -->
<!-- ::: -->

<!-- ```{r} -->
<!-- CV %<>% print_section('data_science_writings') -->
<!-- ``` -->



<!-- Selected Press (About)  {data-icon=newspaper} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %<>% print_section('about_me_press') -->
<!-- ``` -->


<!-- <br> -->
<!-- <br> -->


<!-- Selected Press (By)  {data-icon=newspaper} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %<>% print_section('by_me_press') -->
<!-- ``` -->



**Selected Manuscripts, Publications, and Posters** {data-icon=book}
--------------------------------------------------------------------------------

<!-- Manuscripts in Preparation {data-icon=pencil-square} -->
<!-- -------------------------------------------------------------------------------- -->
<!-- ```{r} -->
<!-- CV %<>% print_section('academic_manuscripts') -->
<!-- ``` -->

_Manuscripts Under Review or Revision_ {data-icon=file-text}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('academic_underreview')
```


_Published Publications_ {data-icon=institution}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('academic_articles')
```

_Posters_ {data-icon=columns}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('academic_presentations')
```

**Honors and Awards** {data-icon=star}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('honors_awards')
```


**Memberships** {data-icon=users}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('professional_memberships')
```

**Services** {data-icon=tasks}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('professional_services')
```

```{r}
CV %<>% print_links()
```

<!-- These breaks just force a new page so section doesnt get cut off -->

**Technical and Research Skills** {#skills}
--------------------------------------------------------------------------------

```{r}
CV %>% print_skill_bars()
```


\pagebreak

References {data-icon=users}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_references()
```